Goal Recognition as Planning with Unknown Domain Models

### 2019-01-30 doc/ijcai-19-goalRecognition/goalRecognition.tex
first comments on goal recognition design added to the ijcai19 paper on goal recognition

\subsubsection{Soundness and completeness}

@@

>>>>

@@

Our approach for {\em planning with an unknown domain model} is also related to {\em goal recognition design}~\cite{KerenGK14}. The reason is that we are encoding the space of propositional schemes as state variables of the planning problem (we encode the {\em empty} action model with no preconditions and no effects at the initial state) and provide actions to modify the value of this state variables (the action model) to enable the {\em goal recognition} process. With this regard {\em goal recognition design} applied to our approach would compute the action model that allows to distinguish the best among the possible goals to be recognized.
